Automated Formal Synthesis of Provably Safe Digital Controllers for Continuous Plants

### 2019-01-30 automatica/paper.tex
results and tweaks

Our benchmark suite consists of \note{update} 20 SISO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal}.
The models are discretized with sampling times ranging from 1.5s to 0.005s, and if CEGIS is unable to 
synthesise a controller for a given sampling time, CEGIS heuristically selects a new sampling time \note{do we, still? Yes, each benchmark has up to 8 time discretisations, that we run through in the order they are written in the benchmark. ``heuristically'' is a euphemism for the fact the order is not consistent for each benchmark and we dont run through them in e.g., increasing order.}.

@@

The \textit{antenna} benchmark (\#2) 
describes the dynamics of the azimuth angle of an antenna 
motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. \\

@@

The \textit{Chen\_ex1} and \textit{Chen\_ex3}
benchmarks correspond to higher-order control system 

@@

models employed as case studies for model-order reduction techniques~\cite{CHEN1979389}.  \\

@@

The benchmarks \textit{Cruise}~\cite{Franklin15} and \textit{CruiseHSCC}~\cite{Astrom08} deal with automotive cruise control models, 

@@

The \textit{guidance chen} benchmark ( is a high-order system model used by Chen et al.~\cite{CHEN1979389} to evaluate 
model-order reduction techniques; it models a guidance control system, 
which is used to determine the path of an autonomous vehicle \note{This is similar to the two benchmarks above?}. \\ 

@@

The \textit{Invpendulum\_pendang}  

@@

The \textit{magpointer}  describes a magnetic pointer, 

@@

@@

%The \textit{USCG cutter tampa heading angle} plant describes the heading angle dynamics of a Coast 
%Guard cutter. The \textit{satellite attitude control system} plant describes the dynamics of a satellite 
%attitude, {\it i.e.}, the orientation angles. An attitude control system must maintain the desired 
%orientation of a satellite with respect to an 
%inertial frame during all the excursion.

@@

We provide the results in Table~\ref{tab:results}, where: 
\textit{Benchmark} is the name of the corresponding benchmark; 
\textit{Order} is the number of continuous variables of the model; 
$\mathcal{F}_{\langle I_p,F_p \rangle}$, where $I_p$ and $F_p$ indicate the integer and fractional parts,  
and $\mathcal{F}_{\langle E_p,M_p \rangle}$, where $E_p$ and $M_p$ indicate the exponent and mantissa part, 
are the fixed- and floating-point precisions used to model the plant, respectively; 
and \textit{Time} is the total time required to synthesize a controller for the given plant.    
Timeouts are indicated by~\xmark, while failures to synthesise the digital controllers are indicated by $\dagger$ \note{no such instances}.  
The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
chosen to be $I_c = 8$, $F_c = 8$ for fixed-point, whereas  
$\mathcal{F}_{\langle E_c, M_c \rangle}$ is chosen to be $W_c = 6$ and $F_c = 10$
for half-precision floating-point format.

We separate our evaluation into two sets of results: fixed- and floating-point. 
We are able to synthesise more floating-point controllers than fixed-point controllers, likely because the
floating-point controllers are at a higher precision than the fixed-point ones. It may be that the precision of the fixed-point
controllers is too low to be able to meet the safety specification. The floating-point controllers in general take longer to synthesise
than the fixed-point ones. There is one exception to this, which is due to the fact that it is not guaranteed that a controller
exists for all the time discretizations we give the algorithm and, in this case, the fixed-point algorithm might be forced to try more time discretizations
than the floating-point algorithm because a fixed-point controller lacks the precision to control the system under the first (larger) time discretizations. 
%For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based
%back-end is faster than the basic multi-staged verification approach; \textcolor{blue}{additionally, 
%from 26 benchmarks, we observed that the abstraction-based back-end finds a solution for more benchmarks 
%(14) than the multi-staged back-end (13)}.
%%\note{we should clarify that this is out of 26 in total, not 191?}  
%In direct comparison, the abstraction-based approach is on average able to find a
%solution in approximately 53\% of the time required using the multi-staged
%back-end, and has a median run-time 0.5\,s, which is twenty times smaller
%than the multi-staged approach.  The two back-ends complement each other in terms of 
%benchmark coverage, and together solve 58\% of the benchmarks \note{only? this does not sound much really}.  
%%
%For the majority of the benchmarks with {\it floating-point} implementation, 
%we also observe that the abstraction-based back-end is much faster than the basic multi-staged verification approach, 
%but both back-ends find the same amount of solutions (13).  
%In direct comparison, the abstraction-based approach is on average able to find a
%solution in approximately 50\% of the time required using the multi-staged
%back-end, and has a median run-time 0.6\,s, which is forty times smaller
%than the multi-staged approach.  The two back-ends complement each other in
%benchmark coverage and together solve 54\% of the benchmarks \note{somewhat underwhelming}.

%\begin{table*}
%\centering
%\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
%%
%\hline
%\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
%   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle E_p, M_p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
%1  & Acrobot     & 4 & 8,8 & 61959.4\,s &  & ~\xmark & & ~\xmark &  & ~\xmark \\
%2  & Antenna     & 6 &  & ~\xmark &  & ~\xmark & & ~\xmark & & 2903s~\xmark\\
%3  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark & & ~\xmark & & ~\xmark\\
%4  & Bioreact    & 3 & 8,8 & 11.5\,s & 6,10 &14.6\,s & 24,14 & 0.4\,s & 6,10 & 0.5\,s\\
%5  & Chen\_ex1   & 3 & 8,8 & 10.3\,s  & 6,10 & 9.2\,s & & ~\xmark & 6,10 & 1.4\,s\\
%6  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 4683.8\,s &  & ~\xmark & & ~\xmark\\
%7  & Chen\_ex3   & 7 &   & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
%9  & Cruise      & 1 & 8,8 & 9.6\,s & 6,10 & 6.5\,s & 24,14 & 0.3\,s& 6,10 & 0.3\,s\\
%10 & CruiseHSCC & 1 & 8,8 & 9.6\,s & 6,10 & 6.6\,s &  24,14 & 0.3\,s & 6,10 & 0.3\,s \\
%11 & Cstr & 3 & & ~\xmark & & ~\xmark & & ~\xmark & & 181s~\xmark\\
%12 & Cstrtmp  & 3 &  & ~\xmark & & ~\xmark & 24,14 & 0.5\,s & & ~\xmark\\
%13 & DCmotor   & 2 & 8,8  & 11.3\,s & 6,10 & 7.8\,s & 24,14 & 0.4\,s & 6,10 & 0.5\,s (4.0\,s) \\
%14 & Flexbeam   & 6 & & ~\xmark & & ~\xmark & 24,14 & 72.1\,s & & ~\xmark\\
%15 & Guidance chen  & 5 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
%16 & Helicopter   & 3 & 8,8 & 13.8\,s & 32,23 & 148\,s & 24,14 & 0.8\,s& 6,10 & 1.1\,s (56.6\,s)\\
%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
%18 & Invpendulum\_pendang & 2 & 24,12 & 9.8\,s & 6,10 & 28.2\,s & 24,14 & 0.4\,s & 6,10 & 0.5\,s\\
%19 & Magpointer   & 2 & 8,8 & 10.1\,s & 6,10 & 20.4\,s & 24,14  & 1\,s& 6,10 & 1.3\,s (\xmark)\\
%20 & Magsuspension  & 2 & 12,12  & 22.2\,s  & 6,10 & 34.8\,s & 24,14 & 0.5\,s & 6,10 & 0.6\,s (\xmark)\\
%21 & Pendulum   & 2 & 8,8 & 8.5\,s & 32,23 & 24\,s & 24,14 & 0.4\,s & 6,10 & 0.5\,s (2.4\,s)\\
%22 & Regulator   & 5 & & ~\xmark & & ~\xmark & &~\xmark  & & 529s~\xmark\\
%23 & Springmassdamper & 2 & & ~\xmark & & ~\xmark & & ~\xmark & & 14.1s~\xmark\\
%24 & streamdrum   & 3 & 8,8  & 332.5\,s & 6,10 & 590.5\,s & 24,14 & 0.7\,s & 6,10 &1.3\,s\\
%25 & Suspension  & 4 & 8,8  & 17.2\,s & 6,10 &1373\,s & 56,30 & 15.3\,s & 6,10 & 4.4\,s (313.6\,s)\\
%26 & Tapedriver   & 3 & 8,8  & 8.2\,s & & ~\xmark & 64,22 & 2.1\,s & 6,10 & 1.1\,s (6.0\,s)\\
%\hline
%%
%\end{tabular}
%\vspace{0.05in}
%\caption{Experimental results\label{tab:results}}
%\end{table*}

\begin{table*}
\centering
\begin{tabular}{| l | c | c | r | c | r |}
%
\hline
% \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Run-time} \\
 Benchmark  &  Order  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Time & $\mathcal{F}_{\langle E_p, M_p \rangle}$ & Time \\\hline
%1  & Acrobot     & 4 & 8,8 & 61529.8\,s &  & ~\xmark \\
 Antenna     & 6 &  & ~\xmark & 6,10 & 817.4\,s \\
%2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
 Bioreact    & 3 & 8,8 & 11.5\,s & 6,10 &23.6\,s \\
 Chen\_ex1   & 3 & 8,8 & 10.3\,s  & 6,10 & 12.7\,s \\
%4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 3535s.1\,s \\
 Chen\_ex3   & 7 & 8,8  & 11.4\,s & 6,10 & 59.1\,s \\
%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
 Cruise      & 1 & 8,8 & 9.7\,s & 6,10 & 10.3\,s \\
 CruiseHSCC & 1 & 8,8 & 9.7\,s & 6,10 & 10.3\,s  \\
 Cstr & 3 & & ~\xmark & 6,10 & 21.4\,s \\
 Cstrtmp  & 3 & 8,8 & 12.5\,s &6,10 & 15.4\,s \\
 DCmotor   & 2 & 8,8  & 10.0\,s & 6,10 & 11.4\,s  \\
%11 & Flexbeam   & 6 & & ~\xmark & 16, 10 & 10916.1\,s \\
%12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
 Helicopter   & 3 &  & ~\xmark & 6,10 & 32.0\,s \\
%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
 Invpendulum\_pendang & 2 & 8,8  & 10.7 & 6,10 & 14.8\,s\\
 Magpointer   & 2 &  & ~\xmark & 6,10 & 86.0\,s \\
 Magsuspension  & 2 & 12,12  & 39.0\,s  & 6,10 & 43.2\,s \\
 Pendulum   & 2 & 8,8 & 13.2\,s & 6,10 & 16.6\,s\\
 Regulator   & 5 & 8,8 & 1532.7\,s & 6,10 & 999.6\,s\\
 Springmassdamper & 2 & & ~\xmark &6,10 & 24.2s \\
 Steamdrum   & 3 & 8,8  & 700.9s & 6,10 & 24.4\,s \\
 Suspension  & 4 & 8,8  & 11.4\,s & 6,10 &15.4\,s \\
 Tapedriver   & 3 & 8,8  & 11.4\,s &6,10 & 13.3\,s \\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results \note{expand description (short, crisp)}\label{tab:results}}
\end{table*}

The mean run-time for the successful benchmarks is 152.6\,s for fixed-point and 117.5\,s for floating-point implementations, respectively.  
The median run-time for the successful benchmarks is 16\,s for fixed-point and 11\,s for floating-point implementations, respectively.
We consider these times to be short enough to be of practical use to control engineers, and thus affirm the validity of EG1.

\textcolor{blue}{We fail to synthesise a controller for several instances.}  
The completeness threshold may be too large, thus causing a timeout \note{but timeouts are handled separately than failures?}, 
or a controller simply may not exist for a benchmark at a given time discretisation and required controller precision. 
Yet another source of incompleteness is the inability of the {\sc synthesize} phase to use a large enough precision for the plant model.

@@

%-------------------------------
\subsection{Threats to validity \note{generality?}}
\label{exp:threats-to-validity}
%-------------------------------

@@

\textit{Plant precision and discretization heuristics:} Our algorithm to
select suitable finite-precision arithmetic to model the plant behavior 
increases the precision by 8 bits at each step 
in order to be compliant with the CBMC type API. 
Similarly, for discretization, we run multiple discretizations for each
benchmark and retain the fastest run.
This works sufficiently well for our benchmarks, but
performance may suffer in some cases, for example if the completeness
threshold is high.

>>>>

Our benchmark suite consists of 19 SISO case studies extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal}. 
The models are discretized with sampling times ranging from 1s to 0.0001s. CEGIS initially starts with the coarsest discretisation (i.e., 1s sampling time), and if it fails to find a controller, reduces the sampling time.

@@

%The \textit{antenna} benchmark (\#2) 
%describes the dynamics of the azimuth angle of an antenna 
%motion system composed by a gearbox, a DC motor and amplifiers~\cite{gajic2008optimal}. \\

@@

The \textit{Chen}
benchmark correspond to a higher-order control system 

@@

model employed as a case study for model-order reduction techniques~\cite{CHEN1979389}.  \\

@@

The benchmarks \textit{Cruise 1}~\cite{Franklin15} and \textit{Cruise 2}~\cite{Astrom08} deal with automotive cruise control models, 

@@

%The \textit{guidance chen} benchmark ( is a high-order system model used by Chen et al.~\cite{CHEN1979389} to evaluate 
%model-order reduction techniques; it models a guidance control system, 
%which is used to determine the path of an autonomous vehicle \note{This is similar to the two benchmarks above?}. \\ 

@@

The \textit{inverted pendulum} benchmark  

@@

The \textit{magnetic pointer} benchmark  describes a magnetic pointer, 

@@

The \textit{satellite attitude control system} plant describes the dynamics of a satellite 
attitude, {\it i.e.}, the orientation angles. An attitude control system must maintain the desired 
orientation of a satellite with respect to an 
inertial frame during all the excursion. 

@@

The \textit{USCG cutter tampa heading angle} plant describes the heading angle dynamics of a Coast 
Guard cutter.

@@

We provide the results in Table~\ref{tab:results}, where: 
\textit{Benchmark} is the name of the corresponding benchmark; 
\textit{Order} is the number of continuous variables of the model; 
$\mathcal{F}_{\langle I_p,F_p \rangle}$, where $I_p$ and $F_p$ indicate the integer and fractional parts,  
and $\mathcal{F}_{\langle E_p,M_p \rangle}$, where $E_p$ and $M_p$ indicate the exponent and mantissa part, 
are the fixed- and floating-point precisions used to model the plant, respectively; 
and \textit{Time} is the total time required to synthesize a controller for the given plant.    
Timeouts are indicated by~\xmark.  
The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
chosen to be $I_c = 8$, $F_c = 8$ for fixed-point, whereas  
$\mathcal{F}_{\langle E_c, M_c \rangle}$ is chosen to be $W_c = 6$ and $F_c = 10$
for half-precision floating-point format.

We separate our evaluation into two sets of results: fixed- and floating-point. 
We present a selection of case-studies that we are able to solve either for floating-point or fixed-point. 
Given a time discretisation, the floating-point controllers in general take longer to synthesise
than the fixed-point ones. However, the fixed-point algorithm is often forced to try more time discretisations, because the fixed-point controller
lacks the precision to control the system at the coarser time discretisation.
%For the majority of the {\it fixed-point} benchmarks, we observe that the abstraction-based
%back-end is faster than the basic multi-staged verification approach; \textcolor{blue}{additionally, 
%from 26 benchmarks, we observed that the abstraction-based back-end finds a solution for more benchmarks 
%(14) than the multi-staged back-end (13)}.
%%\note{we should clarify that this is out of 26 in total, not 191?}  
%In direct comparison, the abstraction-based approach is on average able to find a
%solution in approximately 53\% of the time required using the multi-staged
%back-end, and has a median run-time 0.5\,s, which is twenty times smaller
%than the multi-staged approach.  The two back-ends complement each other in terms of 
%benchmark coverage, and together solve 58\% of the benchmarks \note{only? this does not sound much really}.  
%%
%For the majority of the benchmarks with {\it floating-point} implementation, 
%we also observe that the abstraction-based back-end is much faster than the basic multi-staged verification approach, 
%but both back-ends find the same amount of solutions (13).  
%In direct comparison, the abstraction-based approach is on average able to find a
%solution in approximately 50\% of the time required using the multi-staged
%back-end, and has a median run-time 0.6\,s, which is forty times smaller
%than the multi-staged approach.  The two back-ends complement each other in
%benchmark coverage and together solve 54\% of the benchmarks \note{somewhat underwhelming}.

\begin{table*}
\centering
\begin{tabular}{| l | c | c | r | c | r |}
%
\hline
% \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Run-time} \\
 Benchmark  &  Order  & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Time(s) & $\mathcal{F}_{\langle E_p, M_p \rangle}$ & Time(s) \\\hline
Bioreact	&	2	&	8,8	&	15.35	&	10,6	&	23.76	\\
Chen	&	3	&	8,8	&	11.24	&	10,6	&	14.25	\\
Cruise 2	&	1	&	8,8	&	11.03	&	10,6	&	11.17	\\
Cruise 2	&	1	&	8,8	&	9.93	&	10,6	&	10.54	\\
cstrtmp	&	3	&	12,12	&	90.03	&	10,6	&	321.12	\\
Cstrtmp	&	2	&	8,8	&	18.56	&	10,6	&	16.99	\\
DC motor	&	2	&	8,8	&	10.34	&	10,6	&	12.32	\\
Helicopter	&	3	&	16,16	&	1116.08	&	10,6	&	168.43	\\
Inverted pendulum	&	2	&	12,12	&	16.01	&	10,6	&	18.73	\\
Magnetic pointer	&	3	&	12,12	&	1071.02	&	10,6	&	207.60	\\
Magnetic suspension	&	3	&	20,20	&	56.9	&	10,6	&	998.3	\\
Pendulum	&	2	&	8,8	&	11.74	&	10,6	&	13.69	\\
Regulator	&	5	&	10,16	&	190.28	&		&	~\xmark	\\
Satellite	&	2	&	8,8	&	13.91	&	10,6	&	16.92	\\
Spring-mass-damper	&	2	&	12,12	&	16.09	&	10,6	&	23.21	\\
Steam drum	&	3	&		&	~\xmark	&	10,16	&	21.16	\\
Supension	&	4	&	8,8	&	12.40	&	10,6	&	17.03	\\
Tape driver	&	3	&	8,8	&	12.18	&	10,6	&	14.34	\\
USCG tampa	&	3	&	12,12	&	1143.35	&	10,6	&	210.70	\\
% 
%%1  & Acrobot     & 4 & 8,8 & 61529.8\,s &  & ~\xmark \\
%% Antenna     & 6 &  & ~\xmark & 6,10 & 817.4\,s \\
%%2  & Ballmaglev  & 3 &  & ~\xmark &  & ~\xmark \\
% Bioreact    & 3 & 8,8 & 15.3\,s & 6,10 &23.6\,s \\
%% 
% Chen\_ex1   & 3 & 8,8 & 10.3\,s  & 6,10 & 14.3\,s \\
%%4  & Chen\_ex2   & 8& & ~\xmark & 32,23 & 3535s.1\,s \\
%% Chen\_ex3   & 7 & 8,8  & 11.4\,s & 6,10 & 59.1\,s \\
%%8  & Chen\_ex4   & 9 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
% Cruise      & 1 & 8,8 & 9.7\,s & 6,10 & 10.3\,s \\
%% CruiseHSCC & 1 & 8,8 & 9.7\,s & 6,10 & 10.3\,s  \\
% Cstr & 3 & & ~\xmark & 6,10 & 21.4\,s \\
% Cstrtmp  & 3 & 8,8 & 12.5\,s &6,10 & 15.4\,s \\
% DCmotor   & 2 & 8,8  & 10.0\,s & 6,10 & 11.4\,s  \\
%%11 & Flexbeam   & 6 & & ~\xmark & 16, 10 & 10916.1\,s \\
%%12 & Guidance chen  & 5 & & ~\xmark & & ~\xmark \\
% Helicopter   & 3 &  & ~\xmark & 6,10 & 32.0\,s \\
%%17 & Invpendulum\_cartpos & 4 & & ~\xmark & & ~\xmark & & ~\xmark & & ~\xmark\\
% Invpendulum\_pendang & 2 & 8,8  & 10.7 & 6,10 & 14.8\,s\\
% Magpointer   & 2 &  & ~\xmark & 6,10 & 86.0\,s \\
% Magsuspension  & 2 & 12,12  & 39.0\,s  & 6,10 & 43.2\,s \\
% Pendulum   & 2 & 8,8 & 13.2\,s & 6,10 & 16.6\,s\\
% Regulator   & 5 & 8,8 & 1532.7\,s & 6,10 & 999.6\,s\\
% Springmassdamper & 2 & & ~\xmark &6,10 & 24.2s \\
% Steamdrum   & 3 & 8,8  & 700.9s & 6,10 & 24.4\,s \\
% Suspension  & 4 & 8,8  & 11.4\,s & 6,10 &15.4\,s \\
% Tapedriver   & 3 & 8,8  & 11.4\,s &6,10 & 13.3\,s \\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Synthesis times for fixed- and floating-point controllers\label{tab:results}}
\end{table*}

The mean run-time for the successful benchmarks is 225\,s for fixed-point and 125\,s for floating-point implementations, respectively.  
The median run-time for the successful benchmarks is 15.7\,s for fixed-point and 17.8\,s for floating-point implementations, respectively.
We consider these times to be short enough to be of practical use to control engineers, and thus affirm the validity of EG1.

We present in this paper a selection of case studies for which we are able to synthesise controllers. In the full experimental environment, 
which is available to download, we include further case studies that we were unable to synthesise controllers for. This is in many cases
due to timeouts, especially when the completeness threshold is too large, 
or a controller simply may not exist for a benchmark at a given time discretisation and required controller precision. 
Yet another source of incompleteness is the inability of the {\sc synthesize} phase to use a large enough precision for the plant model.

@@

%-------------------------------
\subsection{Threats to generality}
\label{exp:threats-to-validity}
%-------------------------------

@@

\textit{Plant precision and discretization heuristics:} Our algorithm to
select suitable finite-precision arithmetic to model the plant behavior 
increases the precision by 8 bits at each step 
in order to be compliant with the CBMC type API. 
Similarly, for time-discretization, we try a set of pre-defined time discretisations.
This works sufficiently well for our benchmarks, but
performance may suffer in some cases, for example if the completeness
threshold is high.
